---
title: "Supplemental Assignment"
author: "Ajinkya Sheth"
date: "February 14, 2019"
output: 
  html_document:
    smart: no
    df_print: paged
  pdf_document: default
---


##Regression was originally used by Francis Galton to study the relationship between parents and children. He wondered if he could predict a man’s height based on the height of his father? This is the question we will explore in this problem. You can obtain data similar to that used by Galton as follows:

```{r include=FALSE} 
library(UsingR)
height <- get("father.son")
```

## a) (5 pt) Perform an exploratory analysis of the father and son heights. What does the relationship look like? Would a linear model be appropriate here?
```{r}
plot(height$fheight,height$sheight)
```

### Scatter plot between father's height and son's height shows that most data points are concentrated in the middle and linear model could be a rough generalization for the data

## b) (5 pt) Use the lm function in R to fit a simple linear regression model to predict son’s height as a function of father’s height. Write down the model,
## ysheight = β0 + β1 x fheight
## filling in estimated coefficient values and interpret the coefficient estimates.

```{r}
mod <- lm(sheight ~ fheight, data = height)
summary(mod)
```
### Interpretation: A 1 inch increase in father's height leads to 0.51 inch incease in Son's height


## c) (5 pt) Find the 95% confidence intervals for the estimates. You may find the confint() command useful.
```{r}
confint(mod)
```


## d) (5 pt) Produce a visualization of the data and the least squares regression line.
```{r}
plot(mod$model)
abline(mod)
```



## e) (5 pt) Produce a visualization of the residuals versus the fitted values. (You can inspect the elements of the linear model object in R using names()). Discuss what you see. Do you have any concerns about the linear model?
```{r}
names(mod)
```

```{r}
plot(mod$fitted.values,mod$residuals)
```
### Most of the residuals seem to be concentrated between -5 and 5 units. No major concerns over linear model

## f) (5 pt) Using the model you fit in part (b) predict the height was 5 males whose father are 50, 55, 70, 75, and 90 inches respectively. You may find the predict() function helpful.
```{r}

fh <- data.frame(fheight = c(50,55,79,75,90))
res <- predict(lm(sheight ~ fheight, data = height), fh)
res

```


## g) (5 pt) What do the estimates of the slope and height mean? Are the results statistically significant? Are they practically significant?
### Estimate of slope denotes relationship between two variables within the experimental scope. It might be insignificant beyond the observed values
### Estimate of height indicates the value of father's height when son's height is 0. This estimate doesn't have any statistical significance. 